Introducing Distributed Dynamic Data-intensive (D3) Science: Understanding Applications and Infrastructure

### 2015-09-14 3dpas_intro.tex
RC1

\author{Shantenu Jha\affil{1}\corrauth\, Daniel S. Katz\affil{2},
  Andre~Luckow\affil{1}, Omer Rana\affil{3}, Yogesh Simmhan\affil{4}, Neil Chue
  Hong\affil{5}, Simon Dobson\affil{6}}

\address{\affilnum{1}Rutgers University\break
\affilnum{2}University of Chicago \& Argonne National Laboratory\break
\affilnum{3}Cardiff University\break
\affilnum{4}Indian Institute of Science\break
\affilnum{5}University of Edinburgh\break
\affilnum{6}University of St.~Andrews\break
}

@@

  \katznote{need to add a note about the dates in which application data was
    collected?  I'm not sure the numbers are correct today, for example, from
    ATLAS}\jhanote{Fixed. CF ATLAS: I'll ask Kaushik/ATLAS to check}

@@

\section*{Acknowledgements}
This work was sponsored by NSF OCI-1059635 and made possible by the UK e-Science
Institute Research Theme on Dynamic Distributed Data-Intensive Programming
Abstractions and Systems. We thank Jon Weissman and Jon Blower for useful
initial discussions, as well as 3DPAS workshop attendees. Discussions of the
selected applications benefited from the generous help of Adam Barker, Jon
Blower, Julian Borrill, Silvia Delgado Olabarriaga, Steve Fisher, Keith Jackson,
Scott Klasky, Bob Mann, Don Middleton, Kees Nieuwenhuis, Manish Parashar,
Stephen Pascoe, and Jon Weissman, though any errors are the responsibility of
the authors.  Some of the work by Katz was supported by the National Science
Foundation while working at the Foundation; any opinion, finding, and
conclusions or recommendations expressed in this material are those of the
author(s) and do not necessarily reflect the views of the National Science
Foundation.

>>>>

\author{Shantenu Jha\affil{1}\corrauth\, Daniel S. Katz\affil{2},
  Andre~Luckow\affil{1}, Omer Rana\affil{3}, Yogesh Simmhan\affil{4}, \\ Neil Chue
  Hong\affil{5}}

% \author{Shantenu Jha\affil{1}\corrauth\, Daniel S. Katz\affil{2},
%   Andre~Luckow\affil{1}, Omer Rana\affil{3}, Yogesh Simmhan\affil{4}, Neil Chue
%   Hong\affil{5}, Simon Dobson\affil{6}}

%\affilnum{6}University of St.~Andrews\break

\address{\affilnum{1}Rutgers University\break
\affilnum{2}University of Chicago \& Argonne National Laboratory\break
\affilnum{3}Cardiff University\break
\affilnum{4}Indian Institute of Science\break
\affilnum{5}University of Edinburgh\break
}

@@

  % \katznote{need to add a note about the dates in which application data was
  %   collected?  I'm not sure the numbers are correct today, for example, from
  %   ATLAS}\jhanote{Fixed. CF ATLAS: I'll ask Kaushik/ATLAS to check}

@@

\section*{Acknowledgements}
This work was sponsored by NSF OCI-1059635 and made possible by the UK e-Science
Institute Research Theme on Dynamic Distributed Data-Intensive Programming
Abstractions and Systems. We thank Simon Dobson, Jon Weissman and Jon Blower for
useful initial discussions, as well as 3DPAS workshop attendees. Discussions of
the selected applications benefited from the generous help of Adam Barker, Jon
Blower, Julian Borrill, Silvia Delgado Olabarriaga, Steve Fisher, Keith Jackson,
Scott Klasky, Bob Mann, Don Middleton, Kees Nieuwenhuis, Manish Parashar,
Stephen Pascoe, and Jon Weissman, though any errors are the responsibility of
the authors.  Some of the work by Katz was supported by the National Science
Foundation while working at the Foundation; any opinion, finding, and
conclusions or recommendations expressed in this material are those of the
author(s) and do not necessarily reflect the views of the National Science
Foundation.
